---
title: "Bstar FI: World Cup 2026"
author: ""
date: "Updated on `r format(Sys.time(), '%d %b %H:%M')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: false
    theme: lumen
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
require(readxl)
require(knitr)
require(kableExtra)
require(ggplot2)
require(reshape2)
require(gtools)
require(dplyr)
require(tidyr)
if (dir.exists('/Users/andrew/Githubs/Coding/World Cup/world_cup_2026/')) setwd('/Users/andrew/Githubs/Coding/World Cup/world_cup_2026/') #no-op on the github actions runner

eliminated.teams <- c('South Africa','Uruguay','South Korea','Turkiye','Japan','Germany','Netherlands','Ivory Coast','Sweden','Ecuador','Brazil','Mexico','Portugal','USA','Morocco')

AddPoints <- function(group.stage.entry, group.stage.truth){
  # 2026: the entry sheets are ordered by group, but results_2026.csv rows are kept
  # in calendar order, so align picks to results by Match number and score the
  # games that have a result entered, in results-file (calendar) order
  group.stage.entry <- group.stage.entry[match(group.stage.truth$Match, group.stage.entry$Match),]
  idx.played <- which(!is.na(group.stage.truth$Result))
  group.stage.entry <- group.stage.entry[idx.played,]
  group.stage.truth <- group.stage.truth[idx.played,]
  outcome <- (group.stage.entry[,7] == group.stage.truth[,7]) * 1
  score <- (group.stage.entry[,5] == group.stage.truth[,5] &
            group.stage.entry[,6] == group.stage.truth[,6]) * 1
  group.stage.entry$Outcome <- ifelse(is.na(outcome), 0, outcome)
  group.stage.entry$Score <- ifelse(is.na(score), 0, score)
  group.stage.entry$Points <- group.stage.entry$Outcome + group.stage.entry$Score * 2
  group.stage.entry$Outcome <- cumsum(group.stage.entry$Outcome)
  group.stage.entry$Score <- cumsum(group.stage.entry$Score)
  group.stage.entry$Total <- cumsum(group.stage.entry$Points)
  group.stage.entry$Match <- seq_len(nrow(group.stage.entry)) #games played, in calendar order
  return(group.stage.entry)
}

PasteScore <- function(home, away, homescore, awayscore){
  first <- paste0(c(home, " (", homescore, ")"), collapse="")
  last <- paste0(c(away, " (", awayscore, ")"), collapse="")
  paste0(c(first,' v ',last), collapse="")
}

StrikethroughTable <- function(table, eliminatedteams){
  idx.elim <- table[,1] %in% eliminatedteams
  table[idx.elim,] <- lapply(table[idx.elim,], function(x) paste(paste("~~", x, sep=""),"~~", sep=""))
  return(table)
}

CountStringDiff <- function(x,y){
  return(mapply(function(x,y) sum(x!=y),strsplit(x,""),strsplit(y,"")))
}

FirstString <- function(my.string){
    unlist(strsplit(my.string, " "))[1]
}

SecondString <- function(my.string){
    unlist(strsplit(my.string, " "))[2]
}

ThirdString <- function(my.string){
    unlist(strsplit(my.string, " "))[3]
}

FourthString <- function(my.string){
    unlist(strsplit(my.string, " "))[4]
}

Relayout <- function(results){
  # one row per bracket team; derive the count from the outcome-string length
  # (16 in the Round-of-16 sim) so it can't go stale like the old hard-coded 32,
  # which mis-aligned SF/Final/Winner scoring once the bracket shrank below 32
  n <- nchar(as.character(results)[1])
  t(sapply(seq_len(n), function(x) as.numeric(substring(results, x, x))))
}

GetLowerTri <- function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
}

ReorderCorMat <- function(cormat){
  # Use correlation between variables as distance
  dd <- as.dist((1-cormat)/2)
  hc <- hclust(dd)
  cormat <-cormat[hc$order, hc$order]
}
```

```{r analysis, include=FALSE, cache=TRUE, cache.extra=list(tools::md5sum(c('results_2026.csv','results_elim_2026.csv')), tools::md5sum(list.files(pattern = "World_Cup_2026_.*xlsx", ignore.case = TRUE)))}
file.list <- list.files(pattern = "World_Cup_2026_.*xlsx", recursive = FALSE, ignore.case = TRUE)
raw.entries <- lapply(file.list, function(z)
  suppressMessages(as.data.frame(read_excel(z, sheet = 'Group Stage')))[,1:7])
raw.elim <- lapply(file.list, function(z)
  suppressMessages(as.data.frame(read_excel(z, sheet = 'Elimination Rounds')))[,1:9])
raw.entries <- lapply(raw.entries, setNames,
                   c('Match','Group','Home','Away','Home.Goals','Away.Goals','Result'))
raw.elim <- lapply(raw.elim, setNames,
                   c('Team','Code','Group','Group.Finish','Round.of.16','Quarter.Finals','Semi.Finals','Final','Winner'))
#derive any blank Result from the goal picks (the result is fully determined by the score)
raw.entries <- lapply(raw.entries, function(z) within(z, Result <- ifelse(!is.na(Result), Result, ifelse(Home.Goals > Away.Goals, Home, ifelse(Home.Goals < Away.Goals, Away, 'Draw')))))
names(raw.entries) <- names(raw.elim) <- gsub(".xlsx", "", gsub("World_Cup_2026_","",file.list, ignore.case = TRUE))
results <- read.csv('results_2026.csv', stringsAsFactors = FALSE, na.strings = c('NA',''))
results.elim <- read.csv('results_elim_2026.csv', stringsAsFactors = FALSE, na.strings = c('NA',''))

for (i in seq(length(raw.entries))){
  raw.entries[[i]]$Name <- names(raw.entries)[i]
  raw.elim[[i]]$Name <- names(raw.elim)[i]
}

## Group stage
group.stage.totals <- lapply(raw.entries, function(z) AddPoints(z, results))
running.total <- do.call(rbind, lapply(group.stage.totals, tail, 1))[,c(1,8:10,12)]
running.total <- running.total[rev(order(running.total$Total)),]

results.played <- results[!is.na(results$Result),]
game.names <- gsub("\\( ", "\\(",
                   apply(results.played[,c(3:6)], 1,
                         FUN=function(x) PasteScore(as.character(x[1]),
                                                    as.character(x[2]),
                                                    as.character(x[3]),
                                                    as.character(x[4])
                                                    )
                         )
)
num.games.played <- nrow(results.played)

## Elim stage
points.per.round <- c(1,2^(1:5))
#first transform is for points per round. second transform is because picking first place in group stage is worth 1 extra
points.by.player <- lapply(raw.elim, function(z)
  t(apply(z[,4:(ncol(z)-1)]==results.elim[,3:ncol(results.elim)],
          2,
          sum,
          na.rm=T)) *
    points.per.round +
    c(sum((z[,4] == 1) * (results.elim[,3] == 1), na.rm=T),0,0,0,0,0)
)

elim.stages <- data.frame(names(points.by.player), do.call(rbind, points.by.player))
names(elim.stages) <- c('Name',names(results.elim)[3:8])
elim.total <- data.frame(names(points.by.player), do.call(rbind, lapply(lapply(points.by.player, cumsum), last)))
names(elim.total) <- c('Name','Elimination Points')
elim.total <- elim.total[rev(order(elim.total$`Elimination Points`)),]

start <- rep(0, nrow(elim.total))
total.start <- data.frame(elim.total$Name, start)
names(total.start) <- c('Name','Start')
total.start <- merge(total.start, running.total, by='Name')

total.total <- merge(total.start, elim.stages)[,c('Name','Start','Total',names(elim.stages)[2:7])]
names(total.total)[3] <- 'Group.Points'
total.total[,2:ncol(total.total)] <- t(apply(total.total[,2:ncol(total.total)], 1, cumsum))
total.total <- total.total[rev(order(total.total$Winner)),]
total.total <- total.total[,c('Name','Start','Group.Points','Group.Finish','Round.of.16','Quarter.Finals','Semi.Finals','Final','Winner')]

knockout.bracket.known <- TRUE # set TRUE once the Round of 32 bracket is set (groups complete) and fill in r32.bracket.order below
if (knockout.bracket.known) {
  playoff.format <- read.csv('playoff_format.csv')
  playoff.format$Team <- raw.elim[[1]][c(5,10,14,33,13,25,41,29,9,35,1,45,6,42,15,37),c(1)]
# MAKE SURE YOU EDIT THIS NEXT LINE SUCH THAT IT IS IN THE ORDER OF A KNOCKOUT GRAPH
# CHECK raw.elim[[1]][c(5,21,14,33,25,13,29,41,9,35,18,45,6,42,15,37),c(1)]
raw.elim.ordered <- lapply(raw.elim, function(z) z[c(5,10,14,33,13,25,41,29,9,35,1,45,6,42,15,37),c(6:9)]) #see round_16_format.png. since the "bracket" for round of 16 is Uruguay v Portugal and France v Argentina... we select an ordered table of Uruguay, Portugal, France, Argentina, so the possibility for the SF is 1000, 0100, 0010, 0001 etc. 
x.qf <- c('10', '01') # for every game, this is the combination of team 1 win vs team 2 win
x.sf <- c('1000','0100','0010','0001') # only one of each 4 can make the sf
x.gf <- sapply(0:7, function(z) paste(c(rep(0,z),1,rep(0,7-z)),collapse=''))
x.win <- sapply(0:15, function(z) paste(c(rep(0,z),1,rep(0,15-z)),collapse=''))
playoff.qf.outcomes <- apply(permutations(n=2,r=8,v=x.qf,repeats.allowed=T), 1, function(x) paste(x, collapse=''))
playoff.sf.outcomes <- apply(permutations(n=4,r=4,v=x.sf,repeats.allowed=T), 1, function(x) paste(x, collapse=''))
playoff.gf.outcomes <- apply(permutations(n=8,r=2,v=x.gf,repeats.allowed=T), 1, function(x) paste(x, collapse=''))
playoff.win.outcomes <- x.win

#Possible gf, win combs
playoff.gf.and.win <- data.frame(lapply(expand.grid(playoff.gf.outcomes, playoff.win.outcomes), as.character), stringsAsFactors = FALSE)
idx.good <- sapply(1:nrow(playoff.gf.and.win), function(z) CountStringDiff(playoff.gf.and.win[z,1], playoff.gf.and.win[z,2]))==1
playoff.gf.and.win.good <- playoff.gf.and.win[idx.good,]

#canada, morocco, Paraguay, France, USA, Belgium, Portugal, Spain, Brazil, Norway, Mexico, England, Switzerland, Colombia, egypt, argentina
#Possible sf, gf, win combs.
#idx.playoff.sf.outcomes.remaining <- rep(TRUE, length(playoff.sf.outcomes)) #when nothing has been determined
idx.playoff.sf.outcomes.remaining <- substr(playoff.sf.outcomes,1,8) == "00010001" # when some outcomes are determined
#idx.playoff.sf.outcomes.remaining <- playoff.sf.outcomes == "..." #when its over
playoff.sf.gf.win <- data.frame(lapply(expand.grid(playoff.sf.outcomes[idx.playoff.sf.outcomes.remaining], apply(playoff.gf.and.win.good,1,paste,collapse=" ")), as.character), stringsAsFactors=FALSE)
names(playoff.sf.gf.win) <- c('Semi','Final')
playoff.sf.gf.win$Winner <- sapply(playoff.sf.gf.win$Final, SecondString)
playoff.sf.gf.win$Final <- sapply(playoff.sf.gf.win$Final, FirstString)
idx.good <- sapply(1:nrow(playoff.sf.gf.win), function(z) CountStringDiff(playoff.sf.gf.win[z,1], playoff.sf.gf.win[z,2]))==2
playoff.sf.gf.win.good <- playoff.sf.gf.win[idx.good,]

#Possible qf, sf, gf, win combs.
#Check the format of playoff.format to understand this. E.g. if teams 1 and 3 of the first 4 win their R32 games it starts 1010 etc.
#canada, morocco, Paraguay, France, USA, Belgium, Portugal, Spain, Brazil, Norway, Mexico, England, Switzerland, Colombia, egypt, argentina
#idx.playoff.qf.outcomes.remaining <- rep(TRUE, length(playoff.qf.outcomes)) #when nothing has been determined
#idx.playoff.qf.outcomes.remaining <- substr(playoff.qf.outcomes,1,12) == "010101010101" & substr(playoff.qf.outcomes,15,16) == "01"
idx.playoff.qf.outcomes.remaining <- playoff.qf.outcomes == "0101010101011001" #when its over
playoff.qf.sf.gf.win <- data.frame(lapply(expand.grid(playoff.qf.outcomes[idx.playoff.qf.outcomes.remaining], apply(playoff.sf.gf.win.good,1,paste,collapse=" ")), as.character), stringsAsFactors=FALSE)
names(playoff.qf.sf.gf.win) <- c('Quarter','Semi')
playoff.qf.sf.gf.win$Final <- sapply(playoff.qf.sf.gf.win$Semi, SecondString)
playoff.qf.sf.gf.win$Winner <- sapply(playoff.qf.sf.gf.win$Semi, ThirdString)
playoff.qf.sf.gf.win$Semi <- sapply(playoff.qf.sf.gf.win$Semi, FirstString)
idx.good <- sapply(1:nrow(playoff.qf.sf.gf.win), function(z) CountStringDiff(playoff.qf.sf.gf.win[z,1], playoff.qf.sf.gf.win[z,2]))==4
playoff.sf.gf.win.good <- playoff.qf.sf.gf.win[idx.good,]
playoff.sf.gf.win.good.fmt <- lapply(1:nrow(playoff.sf.gf.win.good), function(z) Relayout(playoff.sf.gf.win.good[z,]))
all.player.outcome <- lapply(raw.elim.ordered, function(y) lapply(playoff.sf.gf.win.good.fmt, function(z) sum(apply(z*y,2,sum,na.rm=T)*c(4,8,16,32), na.rm=T)))
names.keep <- names(all.player.outcome)
all.player.outcome.table <- do.call(cbind, lapply(all.player.outcome, unlist))
all.player.total.outcome.table <- all.player.outcome.table + data.frame(t(total.total[order(total.total$Name),5]))[rep(1,nrow(all.player.outcome.table)),]
colnames(all.player.total.outcome.table) <- names.keep
all.player.wins <- table(names.keep[apply(all.player.total.outcome.table, 1, which.max)]) # kept for the must-wins chunk
# split each remaining path's leader(s) into a sole (outright) win vs a shared 1st (tie)
tot.mat <- as.matrix(all.player.total.outcome.table)
row.max <- apply(tot.mat, 1, max)
is.at.max <- tot.mat == row.max
n.leaders <- rowSums(is.at.max)
outright.wins <- colSums(is.at.max & n.leaders == 1)
tied.wins     <- colSums(is.at.max & n.leaders >  1)

win.percs <- do.call(rbind,
                      lapply(1:length(raw.entries), function(z)
                      apply(all.player.total.outcome.table[,z] > all.player.total.outcome.table, 2, sum)
                      )
                    )/nrow(playoff.sf.gf.win.good)
rownames(win.percs) <- colnames(win.percs)
diag(win.percs) <- NA
}
#playoff.sf.gf.win.good[all.player.total.outcome.table$andrew < apply(all.player.total.outcome.table,1,max),]
```

# TLDR Version

# Scoreboard

```{r running_total, include=TRUE, echo=FALSE, warning=FALSE}
running.tally <- merge(running.total[,c(2,5)], elim.stages[,c(1,2,3,4,5,6,7)])
names(running.tally) <- c('Name','Group Stage Games','Bracket Rankings','Final 16 Picks','Round of 16','Quarter Finals','Semi Finals','Final')
totals <- data.frame(Name = running.tally$Name, Total = apply(running.tally[,2:8], 1, sum))
totals <- totals[order(totals$Total),]

running.tally %>%
  tidyr::pivot_longer(-Name) %>%
  mutate(name = factor(name, levels=rev(c('Group Stage Games','Bracket Rankings','Final 16 Picks','Round of 16','Quarter Finals','Semi Finals','Final'))),
         Name = factor(Name, levels=totals$Name)) %>%
  ggplot(aes(x=Name, y=value, fill=name, label=value)) +
  geom_bar(position="stack", stat="identity") +
  scale_y_continuous(sec.axis = dup_axis()) +
  scale_fill_manual(values = rev(c('#1077C3','#49BCE3','#56042C','#FEC310','#10BC10','#BC10BC','#000000')), guide = guide_legend(reverse = TRUE, nrow=2, byrow=TRUE)) +
  geom_text(size = 3, position = position_stack(vjust = 0.5), color='white', alpha=.7) +
  geom_point(data=totals, aes(x=Name, y=Total, label=Total, fill=NULL), show.legend=FALSE) +
  geom_text(data=totals, aes(x=Name, y=Total+3.5, label=Total, fill=NULL), size=3.5) +
  coord_flip() +
  labs(x='', y='', fill='') +
  theme_minimal() +
  theme(legend.position = "top", legend.box="vertical")
```

# The Detail

## Scores By Stage

```{r totaltable, echo=FALSE, results='asis'}
overall.tally <- merge(running.total, elim.stages)[,c(1,5:11)]
names(overall.tally)[2] <- 'Group.Stage'
names(overall.tally)[4] <- 'Final.16.Picks'
names(overall.tally)[5] <- 'Round.of.16'  #if you want the title to mean "qualified for" don't rename, otherwise if you want it to mean "ypou picked this team to win the... then rename
names(overall.tally)[6] <- 'Quarter Finals'
names(overall.tally)[7] <- 'Semi Finals'
names(overall.tally)[8] <- 'Final'

overall.tally$Total <- apply(overall.tally[,2:ncol(overall.tally)], 1, sum)
kable(overall.tally[rev(order(overall.tally$Total)),],
      row.names = FALSE,
      col.names = gsub("\\."," ",names(overall.tally))) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Future Paths To Victory

## Grand winner

Below shows, of all remaining paths, how many each player wins outright (sole
highest score) versus ties for first (level with at least one other player).

```{r num of paths, echo=FALSE, results='asis'}
#andrew wins if Argentina win, or where Spain and Argentina make the final
#sammy wins 75% of cases if England and Spain make the final, and Spain wins the final. in that case, it cannot be that both Argentina and France make the semis (6 paths)
#sammy wins if Morocco and England make the final and Morocco wins (8 paths)
#sammy wins if Belgium and England make the final and Belgium wins, so long as Morocco beats France (4 paths)
#adrian usually wins if England and Spain make the final, and England wins the final
#pickers usually wins if England and Argentina make the semi final in the same bracket, and England wins the final
#elliott wins if France win and Switzerland/Norway make the final
#will wins if France and Argentina makes the final and France wins
#if Morocco/Belgium/Norway/Egypt/Colombia/Switzerland win, and France do NOT make the final, Moodeng wins
#if Morocco/Belgium/Norway/Egypt/Colombia/Switzerland win, and France do make the final, harro wins 
paths.to.victory <- data.frame(Player = names(outright.wins),
                               Outright = as.integer(outright.wins),
                               Tied = as.integer(tied.wins),
                               stringsAsFactors = FALSE)
paths.to.victory <- paths.to.victory[paths.to.victory$Outright + paths.to.victory$Tied > 0,] # drop players who can no longer win or tie
paths.to.victory <- paths.to.victory[rev(order(paths.to.victory$Outright, paths.to.victory$Tied)),]

kable(paths.to.victory, row.names = FALSE,
      col.names = c('Player','Outright win','Tied win')) %>%

  kable_styling(bootstrap_options = c("striped", "hover"))

```

## Must wins

The below table shows which teams must win their next game for you to stay in the comp.

```{r stay_alive, include=TRUE, echo=FALSE}
#idx_col <- 1 #just before or during R16 
idx_col <- 2 #just before or during Qf not really sure
#idx_col <- 3 #just before or during SF

do_or_die <- lapply(1:length(raw.elim), function(y) apply(data.frame(do.call(rbind, strsplit(playoff.sf.gf.win.good[apply(all.player.total.outcome.table, 1, which.max)==y,idx_col],""))), 2, function(z) all(unique(z)=="1"))) # which.max)==1 means "a_lills" wins, and then all(unique(z)=="1") means they are a must advance to QF for you to stay in

names(do_or_die) <- names(raw.elim)
do_or_die <- do_or_die[sapply(do_or_die, function(x) length(x)) > 0]
contested <- apply(do.call(rbind, do_or_die), 2, function(x) length(unique(x)) > 1)
clean_do_or_die <- t(do.call(data.frame, lapply(do_or_die, function(z) paste(playoff.format[,1][unlist(z) & contested], collapse = " & "))))

clean_do_or_die[clean_do_or_die[,1]!="",] %>%

  kable(col.names = 'Must win to stay alive') %>%

  kable_styling(bootstrap_options = c("striped", "hover"))

#apply(data.frame(do.call(rbind, strsplit(playoff.sf.gf.win.good[apply(all.player.total.outcome.table, 1, which.max)==1,2],""))), 2, function(z) all(unique(z)=="1")) # which.max)==1 means "a_lills" wins, and then all(unique(z)=="1") means they are a must advance to SF for you to stay in

#apply(data.frame(do.call(rbind, strsplit(playoff.sf.gf.win.good[apply(all.player.total.outcome.table, 1, which.max)==1,3],""))), 2, function(z) all(unique(z)=="1")) # which.max)==1 means "a_lills" wins, and then all(unique(z)=="1") means they are a must advance to FINAL for you to stay in

#apply(data.frame(do.call(rbind, strsplit(playoff.sf.gf.win.good[apply(all.player.total.outcome.table, 1, which.max)==1,4],""))), 2, function(z) all(unique(z)=="0")) # which.max)==1 means "a_lills" wins, and then all(unique(z)=="0") means they are a must NOT WIN for you to be able to have a path to victory.

```

## Who can you still beat?

Percentage of cases where you beat (or draw with) each player from all possible game outcomes.

-   Once there is a row where a player hits 100 on every square, they have won.

-   If there's a non-symmetry between the x and the y axis, those are ties (e.g. if the table indicates Peter beats John 40% of the time, but John beats Peter 30% of the time, that means they must tie 30% of the time.)

```{r corr, echo=FALSE, fig.align="center", out.width="90%"}
melted_cormat <- melt(win.percs, na.rm = TRUE)

# Heatmap

ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value*100))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "red", high = "blue", mid = "gray75",
   midpoint = 50, limit = c(0,100), space = "Lab",
    name="Percentage\nof\npaths") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1,
    size = 12, hjust = 1))+
 coord_fixed()

ggheatmap + geom_text(aes(Var2, Var1, label = round(value*100,0)), color = "white", size = 3) +
  xlab('Beats this player') +
  ylab('Proportion of times this player') +
theme(
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank())
```

## Group stage worm

```{r tally.graph, echo=FALSE, fig.align="center", out.width="100%"}
tally.graph.data <- do.call(rbind, group.stage.totals)[,c(1,8,12)] %>% group_by(Name)
tally.graph.data$Name <- factor(tally.graph.data$Name, levels=running.total$Name)
tally.graph.data <- tally.graph.data %>% 
  group_by(Match, Total) %>% 
  mutate(Total = Total + (row_number() - (n()/2+0.5))/5,
         Match = Match + (row_number() - (n()/2+0.5))/10) %>% 
  group_by(Name)
ggplot(data=tally.graph.data, aes(x=Match, color=Name, y=Total, label=Name)) +
  geom_step(alpha=.8, linewidth=.85) +
  scale_y_continuous(breaks = seq(from=0,to=max(tally.graph.data[,3]), by=2),
                     limits=c(min(0, min(tally.graph.data[,3])),max(tally.graph.data[,3])+.02),
                     name = '') +
  scale_x_continuous(breaks=seq(num.games.played), labels=game.names[1:num.games.played],
                     name = '') +
  ggrepel::geom_text_repel(data=~filter(., Match==max(Match)), size=2, alpha=.8, nudge_x=4, max.overlaps=50) +
  labs(color='') +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 90, vjust=.5, size=7),
        legend.position = 'none',
        panel.grid.minor.x = element_blank())
```

```{r tally, echo=FALSE}
kable(running.total[,c(1,3:5)], col.names = c("Matches Played","Outcomes","Scores","Points")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Upcoming picks

<!-- ### Quarter final picks -->

<!-- ```{r quarterfinal.picks, echo=FALSE} -->
<!-- all.elim <- do.call(rbind, raw.elim) -->
<!-- qf.picks <- all.elim[!is.na(all.elim$Quarter.Finals) & all.elim$Quarter.Finals == 1, c('Team','Name')] -->
<!-- qf.by.team <- aggregate(Name ~ Team, data=qf.picks, -->
<!--                          FUN=function(z) paste(sort(z), collapse=", ")) -->
<!-- qf.by.team$n <- lengths(strsplit(qf.by.team$Name, ", ")) -->
<!-- qf.by.team <- qf.by.team[order(-qf.by.team$n, qf.by.team$Team), c('Team','Name')] -->
<!-- kable(StrikethroughTable(qf.by.team, eliminated.teams), -->
<!--       row.names = FALSE, -->
<!--       col.names = c("Team","Picked by")) %>% -->
<!--   kable_styling(bootstrap_options = c("striped", "hover")) -->
<!-- ``` -->
### Semi final picks

```{r semifinal.picks, echo=FALSE}
all.elim <- do.call(rbind, raw.elim)
sf.picks <- all.elim[!is.na(all.elim$Semi.Finals) & all.elim$Semi.Finals == 1, c('Team','Name')]
sf.by.team <- aggregate(Name ~ Team, data=sf.picks,
                         FUN=function(z) paste(sort(z), collapse=", "))
sf.by.team$n <- lengths(strsplit(sf.by.team$Name, ", "))
sf.by.team <- sf.by.team[order(-sf.by.team$n, sf.by.team$Team), c('Team','Name')]
kable(StrikethroughTable(sf.by.team, eliminated.teams),
      row.names = FALSE,
      col.names = c("Team","Picked by")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Finals Picks

#### Crowd favourites

```{r crowdsource.finals, echo=FALSE}
all.elim <- do.call(rbind, raw.elim)
elim.count <- aggregate(all.elim[,5:9], FUN=sum, na.rm=T, by=list(all.elim[,1]))
elim.count <- elim.count[with(elim.count,
                              order(-Winner, -Final, -Semi.Finals, -Quarter.Finals, -Round.of.16)),]
kable(StrikethroughTable(elim.count[elim.count$Quarter.Finals > 0,], eliminated.teams),
      row.names = FALSE,
      col.names = gsub("\\.", " ", c("",colnames(elim.count)[2:6])),
      ) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

#### Grand Final Tips

```{r final.picks, echo=FALSE}
finals <- do.call(rbind,
                  lapply(
                    lapply(
                      lapply(raw.elim, '[', c(1,8)),
                      function(z) StrikethroughTable(z, eliminated.teams)),
                        function(z) paste0(z[!(is.na(z[,2]) | grepl("NA", z[,2])),1], collapse=" v ")
                    )
                  )
winner <- do.call(rbind,
                  lapply(
                    lapply(
                      lapply(raw.elim, '[', c(1,9)),
                      function(z) StrikethroughTable(z, eliminated.teams)),
                        function(z) (z[!(is.na(z[,2]) | grepl("NA", z[,2])),1])
                      )
                    )
finals.and.winner <- data.frame(finals, winner, stringsAsFactors=FALSE)
kable(finals.and.winner[order(finals.and.winner$winner),],
      col.names = c("Grand Final Pick","Cup Pick")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```
